Dependent Object Types

### 2012-08-05 article.tex
revised decl sub

The declaration subsumption judgement $\Gamma \ts D \sub D'$ in
\figref{dot-sub} states that in environment $\Gamma$ the
declaration $D$ subsumes the declaration $D'$. There are two rules,
one for type declarations and one for value declarations.  Rule
(\textsc{tdecl-$\sub$}) states that a type declaration $\Ldecl L S U$
subsumes another type declaration $\Ldecl L {S'} {U'}$ if $S'$ is a
subtype of $S$ and $U$ is a subtype of $U'$. In other words, the set
of types between $S$ and $U$ is contained in the set of types between
$S'$ and $U'$.  Rule (\textsc{vdecl-$\sub$}) states that a value
declaration $\ldecl l T$ subsumes another value declaration $\ldecl l
T'$ if $T$ is a subtype of $T'$.

Declaration subsumption is extended a binary relation between
sequences of declarations as follows: $\seq{D} <: \seq{D'}$ iff
$\forall D'_i \exists D_j. D_j \sub D'_i$.

>>>>

The declaration subsumption judgement $\Gamma \ts D \sub D'$ in
\figref{dot-sub} states that in environment $\Gamma$ the declaration
$D$ subsumes the declaration $D'$. There are three rules, one for each
kind (type, value, method) of declarations.  Rule
(\textsc{tdecl-$\sub$}) states that a type declaration $\Ldecl L S U$
subsumes another type declaration $\Ldecl L {S'} {U'}$ if $S'$ is a
subtype of $S$ and $U$ is a subtype of $U'$. In other words, the set
of types between $S$ and $U$ is contained in the set of types between
$S'$ and $U'$.  Rule (\textsc{vdecl-$\sub$}) states that a value
declaration $\ldecl l T$ subsumes another value declaration $\ldecl l
T'$ if $T$ is a subtype of $T'$. Rule (\textsc{mdecl-$\sub$}) is
similar to (\textsc{tdecl-$\sub$}), as the parameter type varies
contravariantly and the return type covariantly.

Declaration subsumption is extended to a binary relation between
sequences of declarations as follows: $\seq{D} <: \seq{D'}$ iff
$\forall D'_i \exists D_j. D_j \sub D'_i$.
